---
title: "SignacSlim Introduction"
author: "Wei Zhang"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect
  pdf_document:
    toc: true

vignette: >
  %\VignetteIndexEntry{SignacSlim Introduction}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
  %\VignetteEncoding{UTF-8}



---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

## SignacSlim Introduction

Single cell ATAC-seq is a promising tool for analyzing transcriptional regulation. In addition, Seurat and Signac provides popular functions for single cell data pre-processing. However, Seurat and Signac depends on too many packages which makes them difficult for other package re-use. Signacslim is a slim version of Signac and it contains many useful methods from Signac and Seurat. SignacSlim depends less packages and can be easily installed compared with Signac and Seurat.

For more information, please see [Signac](https://satijalab.org/signac/)

## How to use SignacSlim

Here is a demo for fast generating feature matrix for scATAC-seq. The algorithm is ultra faster for the situations with more than 10K cells.

```{r}
library(SignacSlim)

fpath <- system.file("extdata", "fragments.tsv.gz", package="SignacSlim")

ppath <- system.file("extdata", "peaks.rds", package="SignacSlim")

peaks <- readRDS(ppath)

fragments <- CreateFragmentObject(fpath)

Matrix <- FeatureMatrix(
  fragments = fragments,
  features = peaks
)

print(Matrix[1:10, 1:4])

```


## Session Info

```{r}
sessionInfo()
```
